### 2017-10-01 TF-vldb2018/subsec-Qinc.tex

In practice, the number of balls with type code ($0,\ldots,0$) is much larger than those balls matching with at least one pattern fragment. By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$),
 redundant computations are avoid.

>>>>

In practice, the number of balls with type code ($0,\ldots,0$) is much larger than that of balls match with some pattern fragments, which is further larger than the number of \affballsx. By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$), redundant computations are avoid.
